---
title: "Graded PS2"
author: "Shih-Chieh Lee"
date: "2023-03-15"
output: pdf_document
---

Load all required packages
```{r, message = FALSE}
library(quantmod); library(xts); library(ggplot2); library(ggpubr)
library(tseries); library(urca); library(tsDyn); library(timetk); library(torch)
library(dplyr)
```

# 1. Data
For future analysis, we need to first read the data and convert it into class txs. The start date of the dataset should be 2012-01-01.
```{r, message = FALSE}
table <- read.csv(file = "Macro_data_can.csv", header =TRUE, sep = ",")
ind <- as.Date(table$Index, format="%Y-%m-%d")
table <- subset(table, select=-c(Index))
Macro_data_can <- xts(x=table, order.by=ind)
start_date <- as.Date("2012-01-01")
can.c <- subset(Macro_data_can, ind >= start_date)
```


# 2. Johansen Test

We now move to run Johansen Cointegration Test
```{r, message = FALSE}
cointegration <- ca.jo(can.c, type="trace", ecdet="trend", spec="transitory")
sc <- summary(cointegration)
sc
```
The output shows that the value of the test statitstic is lowest when r = 3.Hence, we can conclude that the CPI level, the unemployment, the target rate, and the GDP growth rate are all cointegrated.

\newpage

# 3. Time-series Validation:
```{r, warning=FALSE}
vnames <- colnames(can.c)
dat <- as.matrix(na.omit(diff(can.c)))

for (lag in 1:3) {
  print("lag:")
  print(lag)

  for (m in 1:3) {
    
    TT <- nrow(dat)
    T1 <- floor(0.5*TT) # start at 50% of the sample size
    step <- 12 # forecast data horizon for MSE
    tseq <- seq(from=T1, to=TT, by=step)
    tseq <- tseq[-length(tseq)]
    MSE.t <- matrix(0,nrow=tseq[length(tseq)]+step-T1,ncol=length(vnames)) # initialize
    colnames(MSE.t) <- vnames
  
    for (j in tseq) {
  
      # VAR model
      if (m==1) {model <- lineVar(data=dat[1:j-1,], lag=lag, model="VAR", I="diff")
                 fcst <- predict(model, n.ahead=step)}
  
      # VAR model with one threshold
      if (m==2) {model <- TVAR(data=dat[1:j-1,], lag=lag, model="TAR", nthresh=1, trace=F)
                 fcst <- predict(model, n.ahead=step)}    
      
      # VEC model
      if (m==3) {model <- lineVar(data=dat[1:j-1,], lag=lag, r=3, model="VEC")
                 fcst <- predict(model, n.ahead=step)}    
      #Note: TVEC model is not implemented in R for more than 2 variables
  
      js <- j+step-1
      MSE.t[(j-T1+1):(js-T1+1),] <- (dat[j:js,]-fcst)^2
    }
  
    if (m==1) print("VAR")
    if (m==2) print("TVAR")  
    if (m==3) print("VEC")
  
    MSE <- matrix(colMeans(MSE.t), nrow=1)
    colnames(MSE) <- vnames
    print(MSE)
    print(" ")
  }
}
```

# 4. Comment
From the result, we are able to tell that VEC(1) has the lowest MSE for CPI, whereas TVAR(1) has the lowest MSE for GDP and Target Rate. TVAR(2) has the lowest MSE for Unemployment.


